Notes on Twisted SYM and SUGRA

### 2018-09-19 Twist_Notes_18_9.tex
small comments

@@

@@

@@

Now, let's try to write down some of the descriptions of twisted theories that we've been discussing.
\begin{example}[10d $\mc N=1$ Super Yang-Mills]
I'm going to try to write this following the calculation in Baulieu \cite{Baulieu}.  We choose a complex structure on $\RR^{10}$ and decompose the (BRST) fields into irreducible components for the action of $\SU(5)$.  The fields one obtains are
\begin{align*}
A = A_{0, 1} + A_{1, 0} \\
\lambda = \chi + \psi_{1, 0} + B_{0, 2},
\end{align*}
where the subscripts indicate the form type of the component fields.  There's also a ghost $c$, which is a scalar in degree $-1$.  Finally we'll introduce an auxiliary scalar field $h$ (bosonic, in degree 0)   The BRST differential is given by $c \mapsto (\dd c, \ol{\dd} c)$.  Denote this complex by $(\Phi^{\mr{YM}}, \dBRST^{\mr{YM}})$.  The holomorphic twist is only $\ZZ/2\ZZ$-graded, and is given by the identity map from $\psi$ to $A_{1,0}$, the identity map from $h$ to $\chi$, along with the map $\ol \dd$ from $A_{0,1}$ to $B$ \footnote{More precisely, if we're doing perturbation theory around a background connection $A'$ we take the covariant derivative with respect to this $A'$.}.

>>>>

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

@@

\brian{Little confused by this. 
Here are some points to clarify:
\begin{enumerate}
\item Here $\d_{BRST}$ is the {\em linear} term in the BRST differential? 
Maybe it'd be best to write this as $Q$. 
\item For any examples that we want to discuss quantization we probably want to impose the usual geometric restrictions. 
So $(\Phi, Q)$ is an elliptic complex (possibly just $\ZZ/2$ graded).
\item You have in mind $\LL$ that depend more than just jets of fields?
\item Usually, we mod out by total derivatives. 
I would say the {\em theory} is really the element $\int \LL \in \mathcal{O}_{loc}(\Phi) = \dens_M \otimes_{D_M} \sym^\bullet(J \Phi)^\vee$.
\end{enumerate}
}

@@

\brian{
Why is $\Phi \oplus \Phi^![-3]$ $L_\infty$? 
I don't think just the condition $\LL \d_{BRST} = 0$ implies this...
It seems like the thing you want to call a BRST theory is just a local $L_\infty$-algebra. 
Am I missing something really basic?
}

@@

Now, let's try to write down some of the descriptions of twisted theories that we've been discussing.
\begin{example}[10d $\mc N=1$ Super Yang-Mills]
I'm going to try to write this following the calculation in Baulieu \cite{Baulieu}.  We choose a complex structure on $\RR^{10}$ and decompose the (BRST) fields into irreducible components for the action of $\SU(5)$.  The fields one obtains are
\begin{align*}
A = A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5, \fg) \oplus \Omega^{1,0}{\CC^5, \fg)
\lambda = \chi + \psi_{1, 0} + B_{0, 2} \in \Omega^0(\CC^5,
\end{align*}

where the subscripts indicate the form type of the component fields.  There's also a ghost $c$, which is a scalar in degree $-1$.  Finally we'll introduce an auxiliary scalar field $h$ (bosonic, in degree 0)   The BRST differential is given by $c \mapsto (\dd c, \ol{\dd} c)$.  Denote this complex by $(\Phi^{\mr{YM}}, \dBRST^{\mr{YM}})$.  The holomorphic twist is only $\ZZ/2\ZZ$-graded, and is given by the identity map from $\psi$ to $A_{1,0}$, the identity map from $h$ to $\chi$, along with the map $\ol \dd$ from $A_{0,1}$ to $B$ \footnote{More precisely, if we're doing perturbation theory around a background connection $A'$ we take the covariant derivative with respect to this $A'$.}.
